The SMT Competition 2015--2018

### 2019-08-21 2018/report/Reviews_67398_Revised_Response.txt

>  - last paragraph of Section 7.1 that gives motivations for MathTSAT and Z3 to be industrial-strenght tool, and states Z3 training, are either not clear or somehow not convincing as motivations. The paragraph should be clarified, or can be omitted.

TODO

>  - Table 16 should not consider, in my opinion, divisions in which there was only one sound solvers, otherwise the concept of "solved uniquely" is trivially true.

WONTFIX (a unique solution is a unique solution, regardless of *why*
no other solver found a solution; the definition suggested by the
reviewer is not stable under adding a dummy solver that always
responds "unknown"; and some divisions/years in which there was only
one sound solver are explicitly mentioned in the text)

@@

> Section 7
>
> - "are also taking" -> "were taken"

DONE

> - referring in the text to colors may not be a good choice for b/w printing

WONTFIX (there is no reference to colors other than an explanation of
what they mean)

@@

> In the next sentence, commas should be placed before and after "e.g.".

DONE

> For tables 7-9, a smaller font size could be used
> (like in Table 12).

WONTFIX (I tried but didn't manage to make the participants tables fit
on two pages instead of three)

### 2019-08-21 2018/report/SMT-COMP.tex
Clarify scoring rules

The \emph{raw benchmark score} of a solver is a quadruple $\langle
e, n, w, c\rangle$, with
\begin{itemize}[noitemsep]
  \item \makebox[5em][l]{$e \in \{0, 1\}$} number of erroneous results (usually~$e = 0$)
  \item \makebox[5em][l]{$0 \leq n \leq N$} number of correct results (resp.~\emph{reduction} for the \ucoretrack)
  \item \makebox[5em][l]{$w \in [0,T]$} wall-clock time in seconds (real-valued)
  \item \makebox[5em][l]{$c \in [0, 4T]$} CPU time in seconds (real-valued)
\end{itemize}
\noindent
For the \maintrack and \apptrack, $e$ is the number of returned statuses that disagree with the given expected status (as described above, disagreements on benchmarks with unknown status lead to the benchmark being disregarded). For the \ucoretrack, $e$ includes, in addition, the number of returned unsat cores that are ill-formed or are not, in fact, unsatisfiable (as validated by a selection of other solvers selected by organizers).

For the \maintrack and \apptrack,
$N$ is defined as the number of {\tt check-sat} commands, and
$n$ is defined as the number of correct results.
For the \ucoretrack, $N$ is defined as the number of named top-level assertions,
and $n$ is defined as the \emph{reduction}, i.e., the difference between $N$
and the size of the unsat core.

>>>>

The \emph{raw benchmark score} of a solver is a quadruple $\langle
e, n, w, c\rangle$, with
\begin{itemize}[noitemsep]
  \item \makebox[5em][l]{$e\geq 0$} number of erroneous results (usually~$e = 0$)
  \item \makebox[5em][l]{$0 \leq n \leq N$} number of correct results (resp.~\emph{reduction} for the \ucoretrack)
  \item \makebox[5em][l]{$w \in [0,T]$} wall-clock time in seconds (real-valued)
  \item \makebox[5em][l]{$c \in [0, 4T]$} CPU time in seconds (real-valued)
\end{itemize}
\noindent
For the \maintrack and \apptrack, $e$ is the number of returned statuses that disagree with the given expected status; $e \in \{0,1\}$ for the \maintrack.  (As described above, disagreements between solvers on benchmarks with unknown status lead to the benchmark being disregarded.)  For the \ucoretrack, $e$ includes, in addition, the number of returned unsat cores that are ill-formed or are not, in fact, unsatisfiable (as validated by a selection of other solvers selected by organizers).

For the \maintrack and \apptrack,
$N$ is defined as the number of {\tt check-sat} commands ($N=1$ for the \maintrack), and
$n$ is defined as the number of correct results.
For the \ucoretrack, $N$ is defined as the number of named top-level assertions,
and~$n$ is defined as the \emph{reduction}, i.e., the difference between $N$
and the size of the unsat core returned by the solver.
